\LARGE \bf Signal2Image Modules in Deep Neural Networks for EEG Classification

### 2020-11-30 ms.tex
init
fix README.md
simplify Makefile

\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}

@@

\begin{figure}[!t]
	\centering
	\begin{tikzpicture}[]
		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{results/signal-epilepsy}};
		\node[align=left] at (-4.2, 0) {$x_i$};
		\draw[dashed,->] (-4, 0) -- (-3.8, 0);
		\node[draw, minimum height=2.55cm] at (-3.5, 0) {$m$};
		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{results/cnn-epilepsy}};
		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
		\node[draw, minimum height=2.55cm] at (0.1, 0) {$b_{d}$};
		\draw[dashed,->] (0.4, 0) -- (0.6, 0);
		\node[align=left] at (0.8, 0) {$\hat{y_i}$};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.67, 1.1) {\footnotesize Open 0.1\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.74, 0.55) {\footnotesize Closed 0.2\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.78, 0) {\footnotesize Healthy 0.9\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.8, -0.55) {\footnotesize Tumor 34.7\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.9, -1.1) {\footnotesize Epilepsy 64.1\%};
	\end{tikzpicture}
	\caption{High level overview of a feed-forward pass of the combined methods.
	$x_i$ is the input, $m$ is the Signal2Image module, $b_{d}$ is the 1D or 2D architecture `base model' for $d=1,2$ respectively and $\hat{y_i}$ is the predicted output.
	The names of the labels are depicted at the right along with the predictions for this example signal.
	The image between $m$ and $b_{d}$ depicts the output of the one layer CNN Signal2Image module, while the `signal as image' and spectrogram have intermediate images as those depicted at the second and third row of Fig.~\ref{fig:signal2imageoutputs}.
	Arrows denote the flow of the feed-forward pass.
	For the 1D architectures $m$ is omitted and no intermediate image is generated.}
	\label{fig:highleveloverview}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
	\rotatebox[origin=c]{90}{Original Signal}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{results/signal-eyes-open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{results/signal-eyes-closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{results/signal-healthy-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{results/signal-tumor-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{results/signal-epilepsy}
	\end{subfigure}

	\rotatebox[origin=c]{90}{`Signal as Image'}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/signal-as-image-eyes-open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/signal-as-image-eyes-closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/signal-as-image-healthy-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/signal-as-image-tumor-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/signal-as-image-epilepsy}
	\end{subfigure}

	\rotatebox[origin=c]{90}{Spectrogram}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/spectrogram-eyes-open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/spectrogram-eyes-closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/spectrogram-healthy-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/spectrogram-tumor-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/spectrogram-epilepsy}
	\end{subfigure}

	\rotatebox[origin=c]{90}{\hspace{5mm} one layer CNN}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/cnn-eyes-open}
		\caption{Open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/cnn-eyes-closed}
		\caption{Closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/cnn-healthy-area}
		\caption{Healthy}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/cnn-tumor-area}
		\caption{Tumor}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{results/cnn-epilepsy}
		\caption{Epilepsy}
	\end{subfigure}
	\caption{Visualizations of the original signals and the outputs of the S2Is for each class.
	The x, y-axis of the first row are in \SI{}{\micro V} and time samples respectively.
	The x, y-axis of the rest of the subfigures denote spatial information, since we do not inform the `base model' the concept of time along the x-axis or the concept of frequency along the y-axis.
	Higher pixel intensity denotes higher amplitude.}
	\label{fig:signal2imageoutputs}
\end{figure*}

@@

\begin{table*}[!t]
	\caption{Test accuracies (\%) for combined models.
	The second row indicates the number of layers.
	Bold indicates the best accuracy for each base model.}
	\label{table:results}
	\begin{minipage}{\textwidth}
		\setlength\tabcolsep{0.6pt}
		\centering
		\input{results/results.tex}
	\end{minipage}
\end{table*}

@@

\bibliographystyle{IEEEtran}
\bibliography{ms}

>>>>

@@

\begin{figure}[!t]
	\centering
	\begin{tikzpicture}[]
		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{tmp/signal-epilepsy}};
		\node[align=left] at (-4.2, 0) {$x_i$};
		\draw[dashed,->] (-4, 0) -- (-3.8, 0);
		\node[draw, minimum height=2.55cm] at (-3.5, 0) {$m$};
		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{tmp/cnn-epilepsy}};
		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
		\node[draw, minimum height=2.55cm] at (0.1, 0) {$b_{d}$};
		\draw[dashed,->] (0.4, 0) -- (0.6, 0);
		\node[align=left] at (0.8, 0) {$\hat{y_i}$};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.67, 1.1) {\footnotesize Open 0.1\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.74, 0.55) {\footnotesize Closed 0.2\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.78, 0) {\footnotesize Healthy 0.9\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.8, -0.55) {\footnotesize Tumor 34.7\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.9, -1.1) {\footnotesize Epilepsy 64.1\%};
	\end{tikzpicture}
	\caption{High level overview of a feed-forward pass of the combined methods.
	$x_i$ is the input, $m$ is the Signal2Image module, $b_{d}$ is the 1D or 2D architecture `base model' for $d=1,2$ respectively and $\hat{y_i}$ is the predicted output.
	The names of the labels are depicted at the right along with the predictions for this example signal.
	The image between $m$ and $b_{d}$ depicts the output of the one layer CNN Signal2Image module, while the `signal as image' and spectrogram have intermediate images as those depicted at the second and third row of Fig.~\ref{fig:signal2imageoutputs}.
	Arrows denote the flow of the feed-forward pass.
	For the 1D architectures $m$ is omitted and no intermediate image is generated.}
	\label{fig:highleveloverview}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
	\rotatebox[origin=c]{90}{Original Signal}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{tmp/signal-eyes-open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{tmp/signal-eyes-closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{tmp/signal-healthy-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{tmp/signal-tumor-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{tmp/signal-epilepsy}
	\end{subfigure}

	\rotatebox[origin=c]{90}{`Signal as Image'}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/signal-as-image-healthy-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/signal-as-image-tumor-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/signal-as-image-epilepsy}
	\end{subfigure}

	\rotatebox[origin=c]{90}{Spectrogram}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/spectrogram-healthy-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/spectrogram-tumor-area}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/spectrogram-epilepsy}
	\end{subfigure}

	\rotatebox[origin=c]{90}{\hspace{5mm} one layer CNN}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/cnn-eyes-open}
		\caption{Open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/cnn-eyes-closed}
		\caption{Closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/cnn-healthy-area}
		\caption{Healthy}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/cnn-tumor-area}
		\caption{Tumor}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{tmp/cnn-epilepsy}
		\caption{Epilepsy}
	\end{subfigure}
	\caption{Visualizations of the original signals and the outputs of the S2Is for each class.
	The x, y-axis of the first row are in \SI{}{\micro V} and time samples respectively.
	The x, y-axis of the rest of the subfigures denote spatial information, since we do not inform the `base model' the concept of time along the x-axis or the concept of frequency along the y-axis.
	Higher pixel intensity denotes higher amplitude.}
	\label{fig:signal2imageoutputs}
\end{figure*}

@@

\begin{table*}[!t]
	\caption{Test accuracies (\%) for combined models.
	The second row indicates the number of layers.
	Bold indicates the best accuracy for each base model.}
	\label{table:results}
	\begin{minipage}{\textwidth}
		\setlength\tabcolsep{0.6pt}
		\centering
		\input{tmp/results.tex}
	\end{minipage}
\end{table*}

@@

\bibliographystyle{IEEEtran}
\bibliography{ms.bib}
